---
title: "7 - shinobxr_app()"
author: "Théo Tacail"
date: "`r Sys.Date()`" 
output: 
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 2
vignette: >
  %\VignetteIndexEntry{7 - shinobxr_app()}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
options(rmarkdown.html_vignette.check_title = FALSE)
```

----

[Full documentation and tutorials can be found on the isobxr website.](https://ttacail.github.io/isobxr_web/)

----

# Plots with **shinobxr_app**
## Calling the Shiny app
The `shinobxr_app` function calls a **shiny app** plotting interface (html interface accessible with any type of internet browser).

This app allows to create many plots with a series of options for all outputs given by `compose_isobxr`, `sweep_steady` & `sweep_dyn` functions.

This is notably very useful for the complex outputs of `sweep_steady` & `sweep_dyn` functions. 

This app also allows to export a pdf version of the plot.


```{r eval = FALSE, include=TRUE}
# define workdir in which the SERIES directories are found 
# (SERIES directories start with 3_CPS, 4_STD or 4_DYN) 
# for instance:
workdir <- "~/1_ABC_tutorial"

# Launch the shiny app
shinobxr_app()
```


## User interface for plot editing

[Full description of the shiny app is available here.](https://ttacail.github.io/isobxr_web/vgn_09_runShinyPlots.html)
