---
title: "1 - Install isobxr"
author: "Théo Tacail"
date: "`r Sys.Date()`" 
output: 
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 2
vignette: >
  %\VignetteIndexEntry{1 - Install isobxr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, include = FALSE}
#####################################################################################
library(devtools)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

----

[Full documentation and tutorials can be found on the isobxr website.](https://ttacail.github.io/isobxr_web/)

----

The [isobxr](https://ttacail.github.io/isobxr/) package is a set of R tools 
designed to perform and explore stable isotope box modelling 
of open or closed systems.
It provides a ready-to-use tool allowing users to 
develop and test isotopic box models of their system of interest. 
It allows the user to explore the behavior of these systems
in both static (*e.g.*, at steady state) or dynamic modes 
(*e.g.*, in reaction to a perturbation), 
build complex scenarios, and sweep the space of parameters in both static 
and dynamic modes.

----

# Installation

## Install isobxr

The [isobxr](https://ttacail.github.io/isobxr/) is available as a source package 
from [GitHub](https://github.com/).

The installation process can be done as follows:

1. Download and install/update [R](https://cran.r-project.org/) and 
[Rstudio](https://rstudio.com/products/rstudio/download/).

2. Download and install package **devtools** as follows:

```{r eval = FALSE}
install.packages("devtools")
```

3. Download and install [isobxr](https://ttacail.github.io/isobxr/) source package.

```{r eval = FALSE}
devtools::install_github("ttacail/isobxr/isobxr", build_vignettes = TRUE) # FALSE if no pandoc/Rstudio 
```

The [isobxr](https://ttacail.github.io/isobxr/) package is working under
R 3.5.2 to 4.0.4 versions.

It's portability has been proof checked for MacOS (10.12 and 10.13), 
Linux (Ubuntu 20.04.1 LTS) and Windows (7 and 10).

You can load the [isobxr](https://ttacail.github.io/isobxr/) package in R
as follows:
```{r eval = FALSE}
library(isobxr)
```

Here is the package description of the current version, 
where you can find the required minimal versions of dependencies:
```{r eval = FALSE}
packageDescription("isobxr")
```

You can locally browse the vignettes as follows:
```{r eval = FALSE}
browseVignettes("isobxr")
```

## Download templates and tutorials

The user is encouraged to: 

1. download the 
[reference templates](https://ttacail.github.io/source/demos/0_excel_templates.zip).
These files provide the user with formated master files, 
used as entries to the functions and described in this vignette.

2. download the [tutorial files](https://ttacail.github.io/source/demos/1_ABC_tutorial.zip). 
These files provide the user with all master files and R commands 
used throughout all demonstrations shown in the vignettes.


----

